\texttt{ensmallen}: a flexible C++ library for efficient function optimization

### 2018-10-16 doc/mlsys_paper/paper.tex
Minor cleanup to formula

      // Compute the objective function
      double Evaluate(const arma::mat& theta) {
        return arma::accu((y - X * theta) % (y - X * theta));
      }
      // Compute the gradient and store in 'gradient'
      void Gradient(const arma::mat& theta, arma::mat& gradient) {
        gradient = -2 * X.t() * (y - X * theta);
      }
     private:
      arma::mat& X; arma::vec& y;
    };
\end{minted}
\vspace*{-0.4em}
%% CS: the above code is currently shown across two pages - not a clean look.
%% CS: how about we place it in a figure ?

>>>>

      // Compute the objective function
      double Evaluate(const arma::mat& theta) {
        return std::pow(arma::norm(y - X * theta), 2.0);
      }
      // Compute the gradient and store in 'gradient'
      void Gradient(const arma::mat& theta, arma::mat& gradient) {
        gradient = -2 * X.t() * (y - X * theta);
      }
     private:
      arma::mat& X; arma::vec& y;
    };
\end{minted}
\vspace*{-0.4em}
%% CS: the above code is currently shown across two pages - not a clean look.
%% CS: how about we place it in a figure ?
